---
title: "Modeling Smartphone Price Prediction Using Linear Regression"
author: "Annisa Indriani"
date: "2024-10-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import Data

```{r}
library(readr)
data <- read.csv("Cellphone.csv", sep=";")
head(data)
```

## Exploratory Data Analysis

### Check Data Structure 

```{r}
str(data)
```

### Check Summary 

```{r}
summary(data)
```

### Check Missing Values

```{r}
colSums(is.na(data))
```

### Correlation Heatmap

```{r}
library(dplyr)
correlation_matrix <- cor(data %>% select_if(is.numeric))

library(ggplot2)
library(reshape2)
melted_correlation <- melt(correlation_matrix)
ggplot(data = melted_correlation, aes(x = Var1, y = Var2, fill = value)) +
  geom_tile() +
  scale_fill_gradient2(low = 'blue', high = 'red', mid = 'white', 
                       midpoint = 0, limit = c(-1, 1), name = 'Correlation') +
  theme_minimal() +
  labs(title = 'Correlation Heatmap')
```

## Linear Regression Model

### Price + Internal Memory

```{r}
library(lmtest)
m1 <- lm(Price ~ internal.mem, data = data)
summary(m1)
```

From the summary above, we can see that the model is significant because the p-value is less than alpha 0.05. In addition, the variable also has a p-value below 0.05, which means that there is a relationship between internal memory and mobile phone price.

### Price + RAM

```{r}
m2 = lm(Price ~ ram, data = data)
summary(m2)
```

From the summary above, we can see that the model is significant because the p-value is less than alpha 0.05. In addition, the variable also has a p-value below 0.05, which means that there is a relationship between RAM and mobile phone price.

### Price + Battery

```{r}
m3 = lm(Price ~ battery, data = data)
summary(m3)
```

From the summary above, we can see that the model is significant because the p-value is less than alpha 0.05. In addition, the variable also has a p-value below 0.05, which means that there is a relationship between battery and mobile phone price.

### Price + RearCam

```{r}
m4 = lm(Price ~ RearCam, data = data)
summary(m4)
```

From the summary above, we can see that the model is significant because the p-value is less than alpha 0.05. In addition, the variable also has a p-value below 0.05, which means that there is a relationship between internal rear camera and mobile phone price.

### Price + Internal Memory + RAM + Battery + RearCam

```{r}
m5 = lm(Price ~ internal.mem + ram + battery + RearCam, data = data)
summary(m5)
```

From the summary above, we can see that the model is significant as the p-value is smaller than alpha 0.05. In addition, all variables except internal memory have a p-value below 0.05, which means there is a relationship between ram, battery, rear cam and phone price.

### Price + RAM + Battery + RearCam

```{r}
m6 = lm(Price ~ ram + battery + RearCam, data = data)
summary(m6)
```

From the summary above, we can see that the model is significant because the p-value is less than alpha 0.05. In addition, the variable also has a p-value below 0.05, which means there is a relationship between ram, battery, rear cam and phone price.

## Assumptions Test

### Independent

```{r}
dwtest(m1, alternative = "two.sided")
```

```{r}
dwtest(m2, alternative = "two.sided")
```

```{r}
dwtest(m3, alternative = "two.sided")
```

```{r}
dwtest(m4, alternative = "two.sided")
```

```{r}
dwtest(m5, alternative = "two.sided")
```

```{r}
dwtest(m6, alternative = "two.sided")
```

The Durbin-Watson test results for Models 1, 2, 5, and 6 have a p-value of more than alpha 0.05, which indicates that the independence assumption is met. In contrast, for Models 3 and 4, the p-value is less than 0.05, indicating that the independence assumption is not met, and therefore, they cannot be used for further analysis.

### Identic

```{r}
library(car)
```

```{r}
bptest(m1)
```

```{r}
bptest(m2)
```

```{r}
bptest(m5)
```

```{r}
bptest(m6)
```

The Breusch-Pagan test results for Models 1, 2, 5, and 6 have a p-value of more than alpha 0.05, indicating that the identical assumption is met.

### Normality

```{r}
library(nortest)
```

```{r}
e1 <- residuals(m1)
shapiro.test(e1)
```

```{r}
e2 <- residuals(m2)
shapiro.test(e2)
```

```{r}
e5 <- residuals(m5)
shapiro.test(e5)
```

```{r}
e6 <- residuals(m6)
shapiro.test(e6)
```

The Shapiro-Wilk test results for Model 2 have a p-value of more than alpha 0.05, which indicates that the normality assumption is met. Meanwhile, the remaining models do not meet the normality assumption because the p-value is less than 0.05 so they cannot be used for further analysis.

### Multicollinearity

```{r}
vif(m6)
```

A VIF value of less than 10 indicates that there is no multicollinearity in the RAM variable with other variables.

## Goodness of the Model

### MSE

```{r}
mean((e2^2))
```

### RMSE

```{r}
sqrt(mean((e2^2)))
```

### AIC

```{r}
AIC(m2)
```

Although the value of evaluation metrics may not be as good or as small as other models, Model 2 is a model that can be used for analysis because there are no model assumptions that are violated.
